\chapter{$^{154}$Gd Results}
\label{chap:154Gd}

$^{154}$Gd is a transitional nucleus ($\beta_2=0.3105$) with a large number of $0^+$ states identified by $(p,t)$, 16, under 3 MeV\citep{meyer06:_zeroplus}. Eleven of these $0^+$ states are below the pairing gap (the energy required to remove two like nucleons), as shown in Figure \ref{fig:Gd_Sys}. The nature of these $0^+$ states is of interest for this study. The lowest lying excited $0^+$ state in the nucleus has an anomalously large E2 transition to the ground state, as compared with other nuclei in the region, shown in Figure \ref{fig:Gd_Sys}. For this $0^+$ state, there is a question of the state being a $\beta$-vibration built upon the ground state, or the minimum of another shape configuration.

\afterpage{\clearpage\input{154GdTablesAndFigs/154_0_Systematic_Fig.tex}}

The $^{154}$Gd data was taken across three separate runs; one with ICEBall and GEORGINA, and two with ICEBall and Clovershare, in two different configurations, as discussed in Chapter \ref{chap:setup}. The GEORGINA experiment allowed for the HPGe detectors to be closer to the target, at a distance of 30 cm. This experiment yielded the most conversion electron data, and results in this chapter are quoted from that data. Although the Clovershare detectors had to be placed 5-10 cm farther from the target, the larger number of detectors, 7 for the first run and 5 for the second, resulted in better the $\gamma-\gamma$ coincidence data, so identification of transition placements and level populations are confirmed. All of the experiments used the same enriched $^{152}$Sm target of 1.44 $mg/cm^2$ thickness, discussed in Chapter \ref{chap:setup} and shown in Table \ref{tab:target}. A complete catalog of spectra used in the analysis can be found in Appendix \ref{chap:154_spectra}.

\section{Ground State Band Confirmation}
\label{sec:154GS_Confirm}

In the singles spectrum several prominent peaks stand out, as seen in Figure \ref{fig:154Gd_Singles}. In the $\gamma$-spectrum, there are four prominent peaks from 100 to 500 keV. These peaks are the ground state band. The strong peak just beyond 500 keV is the 511 keV annihilation peak, and the peaks below 100 keV are x-rays. In the conversion electron spectrum of Figure \ref{fig:154Gd_Singles}, there are distinguishable peaks until approximately 400 keV, and then again in the range of 550 keV to 650 keV. The peaks up to 400 keV correspond to these same ground-state lines that are prominent in the $\gamma$-spectrum. The $K$ peaks are 51 keV less than the $\gamma$-peak, due to electron binding energy. The $L$ peaks are 8 keV less, while the $M$ peaks and higher electron shells are 1 keV or less different, compared to the energy of the $\gamma$-peak. The peaks in the range of 550 keV to 650 keV correspond to a strong series of $J^{\pi}\rightarrow J^{\pi}$ transitions from the first excited $0^+$ band.

\afterpage{\clearpage\input{154GdTablesAndFigs/154Gd_Singles_Fig}}

These ground state band transitions are known to be pure E2 multipoles, and have been previously measured and identified as such. This makes them excellent for calibration and comparison with calculated theoretical conversion coefficients.

In gated spectra, the internal conversion coefficients for the ground state band were in agreement with theory, after the angular correlation correction, discussed in Section \ref{sec:angular}, was applied. The peaks corresponding to the ground state band did not have contributions from other transitions when gated. In the singles, two of the four ground state band lines overestimated the conversion coefficient, indicating electron contributions from other transitions.  To remove the contributions from other transitions, the $\gamma$-ray had to be distinguishable and identifable. The conversion coefficient was then assumed from theory, and the contribution to the area was calculated to be
\begin{equation}
    \label{eq:ICC_Subtract}
    A_{e} = \alpha \epsilon_{e} \frac{A_{\gamma}}{\epsilon_{\gamma}} C_{\angle}
\end{equation}
where $\epsilon_{i}$ are the efficiencies of the electrons and gammas respectively. $C_{\angle}$ is the angular correction for this particular transition, discussed in Section \ref{sec:angular}.

For the $6_{gs}^+\rightarrow 4_{gs}^+$ and $8_{gs}^+\rightarrow 6_{gs}^+$ transitions, electron contributions from smaller gamma lines of similar energy had to be subtracted. Looking at Figure \ref{fig:154Gd_Singles}, it is clear there are many transitions around the same energy, making determination of the contributing peaks important. Only lines from reactions in the target material will contribute. Potential contribution lines needed to be identified as coming from the reaction. This is done by gating on the lines and identifying them within the known level scheme,  as is discussed in Section \ref{sec:154GS_Gates}. For instance, the 390.73 keV line in Table \ref{tab:154Gd_Contaminants}, was seen in coincidence with the $4^+_{gs}\rightarrow2^+_{gs}$, $6^+_{gs}\rightarrow4^+_{gs}$, $4^+_{0^+_{2}}\rightarrow2^+_{gs}$, $6^+_{0^+_{2}}\rightarrow6^+_{gs}$, $4^+_{0^+_{2}}\rightarrow4^+_{gs}$, $6^+_{0^+_{2}}\rightarrow4^+_{0^+_{2}}$, and $10^+_{0^+_{2}}\rightarrow8^+_{0^+_{2}}$ transitions. The transitions involving the ground state band gave context for approximate $J^{\pi}$, as no ground state band lines were seen above the $6^+$ state.  The transitions between the $0^+_{2}$ band and the ground state band indicates the 390.73 keV line is part of the $0^+_{2}$ band. Finally, seeing both the $6^+_{0^+_{2}}\rightarrow4^+_{0^+_{2}}$, and $10^+_{0^+_{2}}\rightarrow8^+_{0^+_{2}}$ transitions without the intermediate transition, which matched in energy, gave firm identification. Multipolarities could then be assigned based on the known data, and the contribution to the electron peak of interest could be calculated based on the gamma area and theoretical conversion coefficient. Contributions were subtracted off the fitted area of the electron peak, before the conversion coefficient of the ground state line was calculated. The error also includes contributions from the errors of these extra transitions' gamma peaks and the errors on the theoretical $\alpha$ values. 

There were two types of transitions that contributed to the conversion electron peak areas: those of similar energy, and higher energies whose K-electron energies were similar to the L and M peaks of the lines of interest. The peaks are summarized in Table \ref{tab:154Gd_Contaminants}. The electron-shell of the transition is listed in each case, and total $L$ and $M$ contributions are used, without need to look at subshell contributions.  In several transitions, the mixing ratio had to be assumed to get a conversion coefficient for the subtraction.

\afterpage{\clearpage\input{154GdTablesAndFigs/154GdGSBandCorr}}

The $6_{gs}^+\rightarrow 4_{gs}^+$ K-conversion coefficient was 0.0546(1)(14) before contributions from other transitions were taken into account. After subtracting the transitions in Table \ref{tab:154Gd_Contaminants}, the new value is 0.0335(1)$^{+11}_{-10}$, in agreement with previous measurements and theory from BrICC\citep{kibedi08:_BRICC}. Similarly, the $8_{gs}^+\rightarrow 6_{gs}^+$ K-conversion coefficient went 0.0271(2)(7) to 0.0180(2)(5), also in agreement with theory calculations. The contributing transitions that were subtracted are summarized in Table \ref{tab:154Gd_Contaminants}.  The conversion coefficient was then calculated, with an angular distribution correction based on the multipolarity of the transition. The transitions up to the $10_{gs}^+$ are summarized and compared with theory in Table \ref{tab:154Gd_Single_ICC_GS}.

\afterpage{\clearpage\input{154GdTablesAndFigs/154GdGSCoeffs}}

\section{Gates on the Ground State Band}
\label{sec:154GS_Gates}

To confirm the levels populated in the experiment, the $\gamma$-rays of the ground state transitions were used as energy gates. Figures \ref{fig:154_2to0}, \ref{fig:154_4to2}, \ref{fig:154_6to4}, and \ref{fig:154_8to6} are the level scheme result of these gates, with Figures \ref{fig:154_2to0spec}, \ref{fig:154_4to2spec}, \ref{fig:154_6to4spec}, and \ref{fig:154_8to6spec} being the corresponding gated spectra. Band structure in these figures was taken from the data sheets\citep{reich09:_nds_154}. No band assignments were made in this work. In the cases of cascades, secondary gates were done to confirm assignments. The spectra from these gates are available in Appendix \ref{chap:154_spectra}.

Determining which transitions went uniquely into a given ground state level was done by comparing the outgoing ground state transition for that level with the incoming transition i.e. for the $2^+$ level, the $2_{gs}^+\rightarrow 0_{gs}^+$ (123 keV) gate was compared directly with the $4_{gs}^+\rightarrow 2_{gs}^+$ (247 keV) gate. The $\gamma$-spectra corresponding to two of these gates can be seen in Figure \ref{fig:154_GS_Gate}. Lines in the gamma spectrum that were present only in the outgoing spectrum, but not the incoming, were assumed to be populating that level. For example, in Figure \ref{fig:154_GS_Gate}, several areas have been highlighted. The line at 557 keV is present in the $2_{gs}^+\rightarrow 0_{gs}^+$ gate, but not the $4_{gs}^+\rightarrow 2_{gs}^+$ gate. This line corresponds to the $0^+_{2}\rightarrow 2^+_{gs}$ transition, putting it in parallel with the $4_{gs}^+\rightarrow 2_{gs}^+$ transition, explaining why it remains unseen. These identified transitions were then gated on to confirm the assignment, and to search for cascades from higher states.

\afterpage{\clearpage\input{154GdTablesAndFigs/154GdGSGateFig}}

There were nine bands seen in the gating, 4 of which are bands with excited $0^+$ band heads. These are seen in the $2^+_{gs}\rightarrow 0^+_{gs}$ gate (Figures \ref{fig:154_2to0} and \ref{fig:154_2to0spec}). Three of these bands are seen in the $4^+_{gs}\rightarrow 2^+_{gs}$ gate (Figures \ref{fig:154_4to2} and \ref{fig:154_4to2spec}), and two are seen in the $6^+_{gs}\rightarrow 4^+_{gs}$ gate (Figure Figures \ref{fig:154_6to4} and \ref{fig:154_6to4spec}). Only one is seen in the $8^+_{gs}\rightarrow 6^+_{gs}$ gate (Figures \ref{fig:154_8to6} and \ref{fig:154_8to6spec}). This drop off is unsurprising for multiple reasons. Studies have shown the $(\alpha,2n)$ reaction to stop populating spin states with a significant cross section beyond $J^{\pi}=12^+$ \citep{wu93:_a2n}. In the ground state band of $^{154}$Gd, the $12^+$ state sits at 2184.69 keV, giving an approximate cut off for populating higher energy states in the nucleus. Additionally, due to the lack of known higher spin states in the higher energy $0^+$ bands, identification of populating such bands in the higher gates becomes difficult.

\afterpage{\clearpage\input{154GdTablesAndFigs/154Gd2to0Fig.tex}}

\afterpage{\clearpage\input{154GdTablesAndFigs/154Gd4to2Fig.tex}}

\afterpage{\clearpage\input{154GdTablesAndFigs/154Gd6to4Fig.tex}}

\afterpage{\clearpage\input{154GdTablesAndFigs/154Gd8to6Fig.tex}}

\section{Conversion Coefficients from Singles}
\label{sec:154_Conv_Singles}

Conversion coefficients were calculated from the singles spectra. Transitions that could be clearly identified and distinguished are found in Table \ref{tab:154Gd_Single_ICC}. Several transitions with E0 components can be found in Table \ref{tab:154Gd_Single_ICC}. Most of the conversion electrons seen are the $K$-shell electron. These transitions were corrected for angular effects based on the multipolarity of the transition.

Table \ref{tab:154Gd_Single_ICC_Uncorr} conversion coefficients have been left uncorrected in the singles for one of two reasons: either there were multiple known assignments to the gamma-ray energy, or the transition is considered a mixed transition, but no mixing ratio, $\delta$ has been previously measured. For the $3^{+}_{\gamma}\rightarrow 2^+_{0^+_2}$ transition, a mixing ratio, $\delta$, could be calculated by solving the equation
\begin{equation}
    \alpha_{exp}C_{\angle}(\delta)=\frac{1}{1+\delta^2}(\alpha(E2)+\delta^2\alpha(M1))
\end{equation}
where $\alpha_{exp}$ is the uncorrected conversion coefficient, $C_{\angle}(\delta)$ is the angular distribution correction as a function of the mixing ratio, and $\alpha(E2),\alpha(M1)$ are the theoretical conversion coefficients from BrICC\citep{kibedi08:_BRICC}. The upper limit of the experimental value did not yield real values, giving a range of  $-3.46 < \delta < 5.38$.

Table \ref{tab:154Gd_No_Mult_ICC} contains the conversion coefficients that could not be corrected because the transition has no multipole assignment. It contains allowable and reasonable theoretical conversion coefficients to compare the values against, calculated using BrIcc \cite{kibedi08:_BRICC}.

\afterpage{\clearpage\input{154GdTablesAndFigs/154GdSinglesCorr}}

\afterpage{\clearpage\input{154GdTablesAndFigs/154GdSinglesUncorr}}

\afterpage{\clearpage\input{154GdTablesAndFigs/154GdSinglesNoMult}}   

In Table \ref{tab:154Gd_Single_ICC}, there are several conversion coefficients that are high, not only compared to theory, but compared to previous measurements (232, 329, 444, and 557 keV). For the 232 keV transition, the large error hints at a lack of statistics.  For the other three transitions, the transition indicates a change from smaller to larger $J^{\pi}$. The angular distribution correction for such transitions is less than 1, inflating the value. This may be an indication the angular distribution correction is not wholly accurate. Further, due to these values being from singles data, unknown contaminants to the electron spectrum cannot be ruled out. While these transitions were identified clearly and separably, low-intensity gamma-rays may have not have had enough statistics to appear in gated spectra. There are also three transitions that are lower than the theoretical values (515, 873 and 894 keV). In all of these cases, $\delta$ is negative. Finally, there are several $J^{\pi}\rightarrow J^{\pi}$ transitions seen in the singles. For the $4^+_{0^+_2}\rightarrow 4^+_{gs}$ between the first excited $0^+$ band and the ground state band at 676 keV, there is clearly an E0 component, although not as big at that seen by Spits or Gono \cite{spits96:_154gd, gono74:_154gd_e0}. It is a similar situation for the $8^+_{0^+_2}\rightarrow 8^+_{gs}$ at 610 keV compared to Gono. Additionally, there is a $6_{\gamma}^+\rightarrow 6^+_{gs}$ transition at 889 keV that is higher than number from Spits and the theoretical conversion coefficient. The $4^+_{\gamma}\rightarrow 4^+_{gs}$ was also found in gating, as will be discussed in the next section.

In Table \ref{tab:154Gd_Single_ICC_Uncorr}, the $2^+_{2^+_2}\rightarrow 2^+_{0^+_2}$ transition at 715 keV appears to have a large E0 component. This transition is examined in the next section. For the two entangled transitions around 645 keV, the $6^+_{0^+_2}\rightarrow 6^+_{gs}$ transition is likely the dominant contribution, as the measured value in the singles is in good agreement with the measured value in the gated data, see Table \ref{tab:154Gd_6_to_6}. Two separate $\alpha$ values are listed in this part of Table \ref{tab:154Gd_Single_ICC_Uncorr}, as the gamma-rays were separable, but the conversion electron peaks were not.

In Table \ref{tab:154Gd_No_Mult_ICC}, the $4^+_{0^+_6}\rightarrow 4^+_{4^+_1}$ transition at 433 keV either indicates a mixed transition with an E0 component. The angular correction for a pure E2 transition would make the conversion coefficient approximately double the theoretical conversion coefficient from BrICC \citep{kibedi08:_BRICC}. This angular correction is the largest correction that can made. Mixed component angular corrections result in values larger than the theoretical M1 transition. Together, this points toward an E0 component to the transition. Unfortunately, this transitions could not be found in gates, as the levels are too high in energy to be populated significantly enough for gates.

\section{$J^{\pi}\rightarrow J^{\pi}$ Transitions}
\label{sec:154_J2J}

\subsection{$0^{+}\rightarrow 0^{+}$ Identification and Population}

With the large number of $0^+$ states in $^{154}$Gd, our first priority was to identify which bands were populated. Table \ref{tab:0plus_154} contains a list of $0^+$ states from Meyer et al, with indications as to which $0^+$ have been observed outside of the discovery paper, and which have been previously observed in the reaction used in this work \cite{meyer06:_zeroplus}.

\input{154GdTablesAndFigs/154_0plus_table}

Many of the states were left unseen in this work as is to be expected. We have seen all states that were observed previously in $(\alpha,2n)$ experiments, in addition to three other $0^+$ excited states. The energy of the $12^+$ in the ground state band, 2184.69 keV, is the rough cut off for populating states. The levels seen in this work exceed previous $(\alpha,2n)$ experiments and agree with the levels seen in Spits et al, a thermal neutron capture experiment\citep{spits96:_154gd}. Until Spits, there was no known spectroscopy for the 1182, 1573 and 1650 keV states, having only been seen previously in $(p,t)$ and $(t,p)$ experiments. No $(\alpha,2n)$ experiments with $\gamma-\gamma$ coincidence, looking for such levels have been run since Spits et al was published in 1996. The energies of the $0^+\rightarrow0^+$ transitions from these states are marked in the electron singles in Figure \ref{fig:154_e_singles}. The most prominent is the $0^+_{2}\rightarrow0^+_{gs}$ transition. The $0^+_{7}\rightarrow0^+_{3}$ transition is at the energy of the $10^+_{gs}\rightarrow8^+_{gs}$ K-electron energy, and the $0^+_{6}\rightarrow0^+_{3}$ transition is between the $8^+_{gs}\rightarrow6^+_{gs}$ L and M electron energies. The $0^+_{7}\rightarrow0^+_{6}$ transition may be present, but sits on the low energy tail of the $2^+_{gs}\rightarrow0^+_{gs}$ L electron peak. To obtain information in these areas, and for possible $J^{\pi}\rightarrow J^{\pi}$ transitions, energy gates were used. A full list of gates and spectra can be found in Appendix \ref{chap:154_spectra}.

\input{154GdTablesAndFigs/154Gd_e_singles}

\subsection{$J^{\pi}\rightarrow J^{\pi}$ Transitions}

After identification of the bands and transitions, gates were put on the outgoing and incoming transitions of states of interest, namely even-$J^{+}$ states. Gates on incoming transitions did not have enough statistics to extract data on transitions of interest from the resulting spectra. However, gates on outgoing transitions allowed enough statistics to look for transitions from states of the same $J^{\pi}$. In many cases, two separate outgoing transition gates could be used to look at the same state. To look for these transitions of interest, other electron peaks, namely those of the ground state band, were subtracted from the regions of interest as described in Section \ref{sec:upper_limit}. This subtraction technique causes the results to be treated as limits. Tables \ref{tab:154Gd_0_to_0} - \ref{tab:154Gd_6_to_6} are the tabulated results. Where previous measurements have been taken, they are been listed. Additionally, the theoretical conversion coefficients have been listed for $M1$ and $E2$ transitions, as taken from BrIcc \cite{kibedi08:_BRICC}.

\afterpage{\clearpage\input{154GdTablesAndFigs/154Gd0to0}}

As is expected, Table \ref{tab:154Gd_0_to_0} is only lower limits. A lower limit in this table is an indication of the noise in the gamma spectrum that acts as the limit for the ability to see a line in the spectrum. Although $M1$ and $E2$ transitions are not allowed, they have been included in the table for the sake of comparison.  The lower limits, expectedly, rule out the $M1$ and $E2$ transitions. The measured limits agree with the ones seen by Spits \cite{spits96:_154gd}.

\afterpage{\clearpage\input{154GdTablesAndFigs/154Gd2to2}}

In Tables \ref{tab:154Gd_2_to_2}, \ref{tab:154Gd_4_to_4} and \ref{tab:154Gd_6_to_6} many of the transitions could be seen in two different gates. In many cases, only lower limits could be seen due to the noise limit in the gamma spectrum.  In other cases, only upper limits could be seen due to the same effect in the electron spectrum.

\afterpage{\clearpage\input{154GdTablesAndFigs/154Gd4to4}}

\afterpage{\clearpage\input{154GdTablesAndFigs/154Gd6to6}}

The majority of these states do not have lifetimes, so $B(E0)$ values cannot be calculated. However, the relative intensities of these values can be compared, assuming they are coming from the same state, as the lifetime would divide out (see equation \ref{eq:rho_life} and \ref{eq:BE0}). The contributions from the individual components of the transition must be separated out.

To compare the $E0$ components, the other two major contributing components ($M1$ and $E2$) had to be subtracted out. This was done by calculating $\epsilon^2$ via equation \ref{eq:epsilon}. Transitions with known $\delta$ mixing ratios are in Table \ref{tab:154Gd_E0_d}. Transitions without known $\delta$ mixing ratios, had $\delta$ assumed to be 1. In some cases, this left a negative value, which has been excluded from the table of results. These values are listed in Table \ref{tab:154Gd_E0}. The $0^+\rightarrow0^+$ transitions are in Table \ref{tab:154Gd_E0_0}. This subtraction was not done for the $0^+$ transitions, as $M1$ and $E2$ transitions are not allowed. Most of the values calculated are upper or lower limits, as the original $\alpha$ obtained was an upper or lower limit. 

The transitions with prominent E0 components are the $J^{\pi}_{0^+_{2}}\rightarrow J^{\pi}_{gs}$, $2^{+}_{\gamma}\rightarrow 2^{+}_{0^+_{2}}$, $2^{+}_{2^{+}}\rightarrow 2^{+}_{0^+_{2}}$, $2^{+}_{0^+_{6}}\rightarrow 2^{+}_{\gamma}$, $2^{+}_{0^+_{7}}\rightarrow 2^{+}_{\gamma}$, $2^{+}_{0^+_{7}}\rightarrow 2^{+}_{0^+_{2}}$ and $6^{+}_{\gamma}\rightarrow 6^{+}_{0^+_{2}}$ transitions. Several others transitions may have further E0 components, as the upper limit does not rule an E0 component out or a lower limit doesn't give a clear indication of an E0 component.

With these values, two transitions from the same level can be compared using the $B(E0)$ formula to take the energy adjustment into account (equation \ref{eq:BE0}). This ratio must then be corrected by the ratio of the gate efficiencies, as the intensities of the transitions are unknown, and the efficiency correction gives absolute numbers to compare. Because some transitions could be seen in multiple gates, these ratios could be calculated using several corrected numbers. These results are summarized in Table \ref{tab:154Gd_BE0_Comp}.

\afterpage{\clearpage\input{154GdTablesAndFigs/154Gd_E0}}

\afterpage{\input{154GdTablesAndFigs/154Gd_E0_0}}

\afterpage{\clearpage\input{154GdTablesAndFigs/154Gd_E0_d}}

\afterpage{\clearpage\input{154GdTablesAndFigs/154Gd_BE0_Comp}}

\subsubsection{$K^{\pi}=0^+_2$, First Excited $0^+$ Band, 680.6673 keV}

The $J^{\pi}\rightarrow J^{\pi}$ transitions between the first excited $0^+$ band and the ground state band appear to be quite strong. Lifetimes beyond the $4^+$ state in the band are unknown, inhibiting the ability to calculate $\rho^2$ for these transitions. In gating, the $2^+_{0^+_2}\rightarrow 2^+_{gs}$, $4^+_{0^+_2}\rightarrow 4^+_{gs}$, and $6^+_{0^+_2}\rightarrow 6^+_{gs}$ transitions were seen. All three transitions indicated a strong E0 component. The $0^+_{0^+_2}\rightarrow 0^+_{gs}$ and $8^+_{0^+_2}\rightarrow 8^+_{gs}$ transitions could be seen in the singles, but not enough statistics were present in gates, viewable in Appendix \ref{chap:154_spectra} (the relevant gates for the $0^+_{0^+_2}\rightarrow 0^+_{gs}$ transition are 134.8 keV and 850 keV, while the relevant gates for the $8^+_{0^+_2}\rightarrow 8^+_{gs}$ transition are 426.8 keV and 437.7 keV). The $2^+_{0^+_2}\rightarrow 2^+_{gs}$ transition agreed with previous measurements from Spits \citep{spits96:_154gd}. The $4^+_{0^+_2}\rightarrow 4^+_{gs}$ transition appears to be higher than the measurements from Spits and Gono \citep{gono74:_154gd_e0}. Similarly, the $6^+_{0^+_2}\rightarrow 6^+_{gs}$ transition appears to be larger than Gono.

Looking at Table \ref{tab:154Gd_E0_d}, the first $0^+$ excited band to the ground state has several transitions with known mixing ratios and lifetimes. The E0 mixing ratio, $\epsilon^2$ and the matrix element $\rho^2$(E0) are calculated.

\subsubsection{$K^{\pi}=0^+_3$, Second Excited $0^+$ Band, 1182.091 keV}

All of the measurements of transitions coming out of the second excited state were limits. For the $0^+$ state (1182.091 keV), the gates were used to look for the transition to the first excited $0^+$ state. The lower limit on the transition is lower than that previously measured by Spits. The limit in this work comes from the background of the HPGe detector. No further transitions could be seen above $4^+$, as the band is only known up to this $J^{\pi}$.

For the $2^+$ state (1418.16 keV), two transitions were examined, one to the $2^+$ in the first $0^+$ excited state and one to the head of the $\gamma$-band. Each of these transitions was measured with two different gates. The lower limits are consistent with the Spits data. For the transition to the $\gamma$-band, there appears to be an E0 component. The lower limit in the transition to the first excited $0^+$ state is not conclusive.

For the $4^+$ state (1701.39 keV), two transitions were examined, one to the $4^+$ in the first $0^+$ excited state and one to the head of the $\gamma$-band. Each of these transitions was measured with two different gates. These transitions only have upper limits. For the transition to the $\gamma$-band, the upper limit is not close to the M1 conversion coefficient, indicating there may be some E0 strength. This cannot be stated conclusively, as it is only an upper limit. The upper limits in the transition to the first excited $0^+$ state from the two different gates disagree. One upper limit agrees with the previous measurement from Spits, and would indicate there may be E0 strength \citep{spits96:_154gd}. The other upper limit indicates a mixed M1+E2 transition with no or very little E0 strength.

Looking at Table \ref{tab:154Gd_BE0_Comp}, the second $0^+$ excited band seems to strongly favor transitioning to the $\gamma$-band, over transitioning to the first $0^+$ excited band. None of the transitions examined have known mixing ratios, so the $q^2$ and $\alpha q^2$ can be found in Tables \ref{tab:154Gd_E0} and \ref{tab:154Gd_E0_0}. 

\subsubsection{$K^{\pi}=0^+_6$, Fifth Excited $0^+$ Band, 1573.9 keV}

For the $0^+$ state (1573.9 keV), the gates were used to look for the transition to the first and second excited $0^+$ states. The lower limit on the transition to the second excited $0^+$ state is lower than that previously measured by Spits. The limit in this work comes from the background of the HPGe detector.  The transition to the first excited $0^+$ state had not previously been measured, making this lower limit the first measurement. No further transitions could be seen above $4^+$, as the band is only known up to this $J^{\pi}$. The $4^+$ state is not seen, as it is at approximately the same energy as the population cut off.

For the $2^+$ state (1716.050 keV), two transitions were examined, one to the $2^+$ in the first $0^+$ excited state and one to the head of the $\gamma$-band. Each of these transitions was measured with two different gates. The upper limits to the first excited $0^+$ band would indicate a small E0 component if one exists. For the transition to the $\gamma$-band, the values were measurable. The conversion coefficients found in both gates indicate an E0 component. Not enough statistics were present to see any transition between this $2^+$ state and the $2^+$ state of the second excited $0^+$ band.

Looking at Table \ref{tab:154Gd_BE0_Comp}, the fifth $0^+$ excited band seems to favor transitioning to the $\gamma$-band, over transitioning to the first $0^+$ excited band. None of the transitions examined have known mixing ratios, so the $q^2$ and $\alpha q^2$ can be found in Tables \ref{tab:154Gd_E0} and \ref{tab:154Gd_E0_0}. 

\subsubsection{$K^{\pi}=0^+_7$, Sixth Excited $0^+$ Band, 1650.3 keV}

For the $0^+$ state (1650.3 keV), the gates were used to look for the transition to the first and second excited $0^+$ states. The transition to the fifth state would emit an electron lower than the thresholds on the detectors, making the measurement infeasible with the current set up. The lower limit on the transition to the first excited $0^+$ state is lower than that previously measured by Spits, but of similar magnitude. The transition to the second excited $0^+$ state had not previously been measured, making this lower limit the first measurement. No further transitions could be seen above $2^+$, as the band is only known up to this $J^{\pi}$, as proposed by Spits\citep{spits96:_154gd}.

For the $2^+$ state (1775.429 keV), two transitions were examined, one to the $2^+$ in the first $0^+$ excited state and one to the head of the $\gamma$-band. Each of these transitions was measured with two different gates. The lower limits to the first excited $0^+$ band are in good agreement, and would indicate an E0 component if one exists. For the transition to the $\gamma$-band, the values were measurable. The conversion coefficients found in both gates indicate an E0 component. Not enough statistics were present to see any transition between this $2^+$ state and the $2^+$ state of the second excited $0^+$ band.

Looking at Table \ref{tab:154Gd_BE0_Comp}, the sixth $0^+$ excited band seems to favor transitioning to the $\gamma$-band, over transitioning to the first $0^+$ excited band, but as the ratio is a lower limit, this cannot be confirmed. None of the transitions examined have known mixing ratios, so the $q^2$ and $\alpha q^2$ can be found in Tables \ref{tab:154Gd_E0} and \ref{tab:154Gd_E0_0}. 

\subsubsection{$K^{\pi}=2^+$, $\gamma$ Band, 996.264 keV}

Transitions for the $2^+$ (996.264 keV), $4^+$ (1263.778 keV), and $6^+$ (1606.55 keV) to the first excited $0^+$ band could be seen in the gates. The $2^+_{\gamma}\rightarrow 2^+_{0^+_2}$ transition are lower limits, indicating a large E0 component. The $6^+_{\gamma}\rightarrow 6^+_{0^+_2}$ transition shows a similar lower limit, indicating a large E0 component. Conversely, the $4^+_{\gamma}\rightarrow 4^+_{0^+_2}$ transition has upper limits pointing to a largely E2 transition. This makes conclusions difficult to draw.

None of the states in the $\gamma$-band had multiple outgoing transitions measured.  No transitions examined have known mixing ratios, so the $q^2$ and $\alpha q^2$ can be found in Table \ref{tab:154Gd_E0}. 

\subsubsection{$K^{\pi}=2^+_2$, Second Excited $2^+$ Band, 1531.305 keV}

Transitions for the $2^+$ (1531.305 keV) and $4^+$ (1789.17 keV) to the first excited $0^+$ band and $\gamma$-band could be seen in the gates. For the $2^+$ transition to the first excited $0^+$ band, the values are large for both gates, disagreeing with the value found by Spits \citep{spits96:_154gd}. It is worth noting the large error on the values from this work indicates the disagreement may be purely statistical. This would indicate a small E0 component if true. For the transition to the $\gamma$-band, there is one value and one lower limit. The lower limit agrees with the measured value, which is much smaller than Spits, but would indicate an E0 component, as Spits' value does.

The transitions for the $4^+$ state are all upper limits. To the first excited $0^+$ band, the upper limits do not rule out the possibility of an E0 component. For the transition to the $\gamma$-band, the upper limits from the two gates agree, firmly placing the transition as an M1+E2 transition, if not a pure E2.

Looking at Table \ref{tab:154Gd_BE0_Comp}, the second $2^+$ excited band seems to either not favor transitioning to the $\gamma$-band over the first $0^+$ excited band, or prefer the first excited $0^+$ band. None of the transitions examined have known mixing ratios, so the $q^2$ and $\alpha q^2$ can be found in Table \ref{tab:154Gd_E0}. 

\subsubsection{$K^{\pi}=4^+_1$, First Excited $4^+$ Band, 1645.814 keV}

Transitions for the $4^+$ (1645.814 keV) and $6^+$ (1911.544 keV) to the first excited $0^+$ band and $\gamma$-band could be seen in the gates. All the values are upper limits. For the $4^+$ transition to the first excited $0^+$ band, the upper limits are lower than the one set by Spits \citep{spits96:_154gd}. The lower of the two upper limits would indicate a mostly E2 transition. The higher of the two would indicate a mixed M1+E2, with little to no E0 component. The upper limits on the transition to the $\gamma$-band agrees with the value measured by Spits, which would indicate a mixed M1+E2 transition. Without a known mixing ratio, it is not possible to tell if there is an E0 component.

For the $6^+$ state, the upper limits on the transition to the first excited $0^+$ band indicate there may be a small E0 component, as both upper limits are higher than the M1 theory strength. Only one gate could be used to look at the transition to the $\gamma$-band. The upper limit agrees with the previous measurement from Gono, which would indicate an E2 transition \citep{gono74:_154gd_e0}. This work's upper limit does not eliminate the possibility of a mixed transition.

Looking at Table \ref{tab:154Gd_BE0_Comp}, the first $4^+$ excited band seems to favor transitioning to the $\gamma$-band over the first $0^+$ excited band. one of the transitions examined has a known mixing ratio, $\delta^2$, which allows for the calculation of the E0 mixing ratio, $\epsilon^2$, listed in Table \ref{tab:154Gd_E0_d}. For the other transitions, the $q^2$ and $\alpha q^2$ can be found in Table \ref{tab:154Gd_E0}. 